\Huge{\textbf{Using Blockchain to Create a Decentralised Security Model for Distributed Systems}}

### 2021-05-03 paper/paper.tex
Added Ken's improvements

\lstdefinestyle{java}{
	commentstyle=\color{comment},
	stringstyle=\color{string},
	keywordstyle=\color{keyword},
	basicstyle=\footnotesize\ttfamily,
	numbers=left,
	numberstyle=\tiny,
	numbersep=5pt,
	frame=lines,
	breaklines=true,
	prebreak=\raisebox{0ex}[0ex][0ex]{\ensuremath{\hookleftarrow}},
	showstringspaces=false,
	upquote=true,
	tabsize=2,
}

%%%%%%%%%%%%%%%%%%
% TITLE
%%%%%%%%%%%%%%%%%%
\title{\Huge{\textbf{Using Blockchain to Create a Decentralised Security Model for Distributed Systems}}}
\date{April 2021}
\author{
\Large{Adam David Bruce} \\ \texttt{\href{mailto:a.bruce3@newcastle.ac.uk}{a.bruce3@newcastle.ac.uk}}}
\begin{document}
\maketitle

@@

%%%%%%%%%%%%%%%%%%
% AIMS AND OBJECTIVES
%%%%%%%%%%%%%%%%%%
\chapter{Project Aims and Objectives}

\section{Aim} \label{aim}
The original aim for this project was to design and create a decentralised firewall that could communicate knowledge of cyberattacks aimed at universities in real-time, allowing other universities to protect themselves from the same attacks. This system would be distributed, and hence must conform to the previous description of a distributed system in section \ref{distributed}. Following an extensive amount of background reading, there appeared to be no existing implementation or design of such a system which inspired the alteration of the aim to instead focus on designing a protocol and implementing a \gls{stub} to demonstrate the protocol's effectiveness. This project will therefore not be implementing a firewall, but instead a system to coordinate firewalls. Further research determined that \gls{blockchain} was the best choice for the underlying structure for such a protocol, and so this final change shaped the current aim for this project: \textbf{Using Blockchain to Create a Decentralised Security Model for Distributed Systems}.

\section{Objectives}
The following objectives provide an outline for what this project hopes to achieve:

@@

%%%%%%%%%%%%%%%%%%
% BACKGROUND
%%%%%%%%%%%%%%%%%%
\chapter{Background}

@@

\section{Inter-Process Communication (IPC)}
Tanenbaum and Woodhull provide an extremely detailed breakdown of their UNIX based operating system in \say{Operating systems: Design and Implementation} \cite{operatingsystems}. This book covers all aspects of an \acrshort{OS}, providing insightful explanations of the decisions made at every step in the design process. As this project is designed to run as an application, many of the details covered in this publication are irrelevant, however Tanenbaum and Woodhull cover one essential aspect of this project: \acrfull{IPC}. \acrshort{IPC} is a function within many \acrlong{OS}s which enables multiple processes to communicate by passing messages to each other. \acrshort{IPC} will be the technique used to interact with the distributed system, as a client process will use \acrshort{IPC} to issue commands to the \gls{stub}.

@@

@@

@@

@@

In addition to the fail-early principle, each node maintains a log of all complete transactions that have taken place on that node. Once a node receives either an advertisement, or a new rule, it is logged immediately. This means that should the operating system fail, or the system suffers from an unrecoverable fault, the operating system can immediately restart the system (which can run as a daemon) which will then load all known hosts into memory, and rebuild the chain from the transaction log.

@@

The test was carried out by connecting all six nodes to the system, followed by two firewall rule transactions. 
\chapter{Evaluation}

@@

Valgrind is an effective tool and is well recognised for its accuracy and detailed output when a leak is found. It can therefore be trusted that the output pictured above is accurate, and that the software does not contain any memory leaks.

@@

    %\item Evaluate the effectiveness of existing distributed security mechanisms.
    %\item Investigate methods of establishing connections and synchronising computers within distributed systems.
    %\item Understand the structure of \gls{blockchain}s and adapt them for firewall transactions.
    %\item Implement and test relevant resilience, fault tolerance and security mechanisms.
    %\item Compare the use of decentralised security mechanisms.

@@

%\iffalse
\chapter{Framework Source Code}
\lstinputlisting[language=c,style=c,caption=main.c,basicstyle=\ttfamily\scriptsize]{../src/main.c}
\lstinputlisting[language=c,style=c,caption=blockchain.h,basicstyle=\ttfamily\scriptsize]{../src/blockchain.h}
\lstinputlisting[language=c,style=c,caption=blockchain.c,basicstyle=\ttfamily\scriptsize]{../src/blockchain.c}
\lstinputlisting[language=c,style=c,caption=firewall.h,basicstyle=\ttfamily\scriptsize]{../src/firewall.h}
\lstinputlisting[language=c,style=c,caption=firewall.c,basicstyle=\ttfamily\scriptsize]{../src/firewall.c}
\lstinputlisting[language=c,style=c,caption=ipc.h,basicstyle=\ttfamily\scriptsize]{../src/ipc.h}
\lstinputlisting[language=c,style=c,caption=ipc.c,basicstyle=\ttfamily\scriptsize]{../src/ipc.c}
\lstinputlisting[language=c,style=c,caption=net.h,basicstyle=\ttfamily\scriptsize]{../src/net.h}
\lstinputlisting[language=c,style=c,caption=net.c,basicstyle=\ttfamily\scriptsize]{../src/net.c}
\lstinputlisting[language=c,style=c,caption=socket.h,basicstyle=\ttfamily\scriptsize]{../src/socket.h}
\lstinputlisting[language=c,style=c,caption=socket.c,basicstyle=\ttfamily\scriptsize]{../src/socket.c}
%\fi

@@

>>>>

%%%%%%%%%%%%%%%%%%
% TITLE
%%%%%%%%%%%%%%%%%%
\title{\Huge{\textbf{Using Blockchain to Create a Decentralised Security Model for Distributed Systems}}}
\date{May 2021}
\author{
\Large{Adam David Bruce} \\ \texttt{\href{mailto:a.bruce3@newcastle.ac.uk}{a.bruce3@newcastle.ac.uk}}}
\begin{document}
\maketitle

@@

%%%%%%%%%%%%%%%%%%
% AIMS AND OBJECTIVES
%%%%%%%%%%%%%%%%%%
\section{Aims and Objectives} \label{aim}
The original aim for this project was to design and create a decentralised firewall that could communicate knowledge of cyberattacks aimed at universities in real-time, allowing other universities to protect themselves from the same attacks. This system would be distributed, and hence must conform to the previous description of a distributed system in section \ref{distributed}. Following an extensive amount of background reading, there appeared to be no existing implementation or design of such a system which inspired the alteration of the aim to instead focus on designing a protocol and implementing a \gls{stub} to demonstrate the protocol's effectiveness. This project will therefore not be implementing a firewall, but instead a system to coordinate firewalls. Further research determined that \gls{blockchain} was the best choice for the underlying structure for such a protocol, and so this final change shaped the current aim for this project: \textbf{Using Blockchain to Create a Decentralised Security Model for Distributed Systems}.\\\\

The following objectives provide an outline for what this project hopes to achieve:

@@

\section{This Document}
The following chapter will explain the background research conducted before starting this project. Once the necessary research has been documented, the design, implementation and testing of this project will be detailed. Finally, at the end of this document, an evaluation will be conducted followed by a conclusion to identify the success of this project and outline future work.

%%%%%%%%%%%%%%%%%%
% BACKGROUND
%%%%%%%%%%%%%%%%%%
\chapter{Background}
This section details the essential background research for this project. It looks at distributed systems, remote procedure calls, decentralised systems, blockchain, security, firewalls, fault tolerance, computer networks and inter-process communication.

@@

\section{Inter-Process Communication (IPC)}
Tanenbaum and Woodhull provide an extremely detailed breakdown of their UNIX based operating system in \say{Operating systems: Design and Implementation} \cite{operatingsystems}. This book covers all aspects of an \acrshort{OS}, providing insightful explanations of the decisions made at every step in the design process. As this project is designed to run as an application, many of the details covered in this publication are irrelevant, however Tanenbaum and Woodhull cover one essential aspect of this project: \acrfull{IPC}. \acrshort{IPC} is a function within many \acrlong{OS}s which enables multiple processes to communicate by passing messages to each other. \acrshort{IPC} will be the technique used to interact with the distributed system, as a client process will use \acrshort{IPC} to issue commands to the \gls{stub}. \\\\

The background research has identified how this project can utilise all of the mentioned technologies, along with a brief analysis regarding the relevance of each technology to this project.

@@

This section will look at how the project was designed from the ground up to include the relevant features to meet the aim and objectives. The section covers the logical design of the system, protocols and structures used within the system.

@@

This section has provided the foundations for the software and protocol allowing an proof of concept to be implemented in the next chapter.

@@

This section will discuss the different technologies used within the system and how they were incorporated into this project. A detailed analysis is provided whenever a decision was made in regards to using different technologies, tools or languages.

@@

In addition to the fail-early principle, each node maintains a log of all complete transactions that have taken place on that node. Once a node receives either an advertisement, or a new rule, it is logged immediately. This means that should the operating system fail, or the system suffers from an unrecoverable fault, the operating system can immediately restart the system (which can run as a daemon) which will then load all known hosts into memory, and rebuild the chain from the transaction log.\\\\

This section has provided a high-level explanation of how this project was implemented, along with the reasons particular technologies were used. Now a functional implementation has been created, the system can be tested.

@@

The test was carried out by connecting all six nodes to the system, followed by two firewall rule transactions. \\\\

This chapter has provided an overview of how the system will be tested. The next chapter will detail the results of these testing methods, along with a general evaluation of the success of the project

\chapter{Evaluation}

This chapter will detail the successful aspects of the project in addition to identifying where the project could have been improved. Additionally, the results from the previously detailed tests will be used to evaluate the effectiveness of the provided system and implementation.

@@

Valgrind is an effective tool and is well recognised for its accuracy and detailed output when a leak is found. It can therefore be trusted that the output pictured above is accurate, and that the software does not contain any memory leaks.\\\\

Now the system has been evaluated and the results of the testing process have been collected it is clear that the system operates correctly and a successful and functional proof of concept has been created.

@@

This section will conclude the project by identifying whether the original aims and objectives were met, and suggesting future work to improve the proposed system.
    %\item Evaluate the effectiveness of existing distributed security mechanisms.
    %\item Investigate methods of establishing connections and synchronising computers within distributed systems.
    %\item Understand the structure of \gls{blockchain}s and adapt them for firewall transactions.
    %\item Implement and test relevant resilience, fault tolerance and security mechanisms.
    %\item Compare the use of decentralised security mechanisms.

@@

%\iffalse
\chapter{Framework Source Code}
\lstinputlisting[language=c,style=c,caption=main.c,basicstyle=\ttfamily\scriptsize]{../src/main.c}
\lstinputlisting[language=c,style=c,caption=blockchain.h,basicstyle=\ttfamily\scriptsize]{../src/blockchain.h}
\lstinputlisting[language=c,style=c,caption=blockchain.c,basicstyle=\ttfamily\scriptsize]{../src/blockchain.c}
\lstinputlisting[language=c,style=c,caption=firewall.h,basicstyle=\ttfamily\scriptsize]{../src/firewall.h}
\lstinputlisting[language=c,style=c,caption=firewall.c,basicstyle=\ttfamily\scriptsize]{../src/firewall.c}
\lstinputlisting[language=c,style=c,caption=ipc.h,basicstyle=\ttfamily\scriptsize]{../src/ipc.h}
\lstinputlisting[language=c,style=c,caption=ipc.c,basicstyle=\ttfamily\scriptsize]{../src/ipc.c}
\lstinputlisting[language=c,style=c,caption=net.h,basicstyle=\ttfamily\scriptsize]{../src/net.h}
\lstinputlisting[language=c,style=c,caption=net.c,basicstyle=\ttfamily\scriptsize]{../src/net.c}
\lstinputlisting[language=c,style=c,caption=socket.h,basicstyle=\ttfamily\scriptsize]{../src/socket.h}
\lstinputlisting[language=c,style=c,caption=socket.c,basicstyle=\ttfamily\scriptsize]{../src/socket.c}

@@

%\fi
